Finite-state morphological transducers for three Kipchak languages

### 2013-10-08 kipchak-lrec-2013/kipchak-paper.tex
skelington
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@47968 72bbbca6-d526-0410-a7d9-f06f51895060

\documentstyle{article}

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}

@@

@@

@@

@@

>>>>

\documentclass{article}

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{natbib}

\bibdata{kipchak-paper}

@@

\author{Jonathan North Washington \\
Departments of Linguistics and Central Eurasian Studies\\
Indiana University\\
Bloomington, IN 47405 (USA)\\
\texttt{jonwashi@indiana.edu} \and
Ilnar Salimzyanov  \\
Institut für Maschinelle Sprachverarbeitung \\
Universität Stuttgart\\
Stuttgart (Germany) \\
\texttt{ilnar@ilnar} \and 
Francis M. Tyers\\
Departament de Llenguatges i Sistemes Informàtics \\  
Universitat d'Alacant\\
E-03071 Alacant (Spain)\\
\texttt{ftyers@dlsi.ua.es} 
}

@@

\cite{washington2012}
\cite{salimzyanov2013}

\section{Languages}

\subsection{Kazakh}

\subsection{Tatar}

\subsection{Kumyk}

@@

\section{Future work}

@@

\bibliographystyle{lrec2012}
\bibliography{paper}
